---
title: "Text Analytics for Marketing: Group Assignment 1 Understanding Text Data"
author: "Joulia Tout, Alexaxndros Stavropoulos, Ioannis Nikolaidis, Djamila Rocha"
date: "March 31, 2023"
output: pdf_document
---

```{r}
require("knitr")
opts_knit$set(root.dir = "C:/Users/ioann/Desktop")
```

## Introduction

In today's digital age, online reviews have become an essential part of consumers' decision-making processes. As such, analyzing this data has become an important task for businesses looking to understand customer opinions and improve their products or services. In this project, we were challenged to analyze text data using principal component analysis (PCA), multi-dimensional scaling (MDS), sentiment analysis, and latent Dirichlet allocation (LDA). Through this analysis, we aimed to understand the opinions expressed by customers and identifying important topics discussed in the reviews.

```{r}
data <- read.csv("C:/Users/ioann/Desktop/Delta_Airline_Review_Dataset-Asof02172023.csv")
df <- data[c(1,2,8)]
df_verified <- df[grepl("Trip Verified", df$reviews), ]
df_verified$reviews <- gsub("✅ Trip Verified \\| ", "", df_verified$reviews)
df <- df_verified
df$star.rating <- as.factor(df$star.rating)


```

## Data Description

For this analysis, textual data from the Delta airline reviews was utilized. This dataset contained a starbased rating scale, going from 1 to 10 , 10 being the best possible rating score. Moreover, these star ratings were paired with textual reviews, pertaining to individual customer IDs. Furthermore, two versions of the dataset were formed. One version remained unstemmed and punctuated, as it was going to be utilized in the sentiment analysis in the subsequent stages. A second, fully cleaned vector representation version was created for the remainder of the analysis; this dataset was fully cleaned. The process of cleaning, included the removal of punctuation, stemming of words, tokenization, and removal of stop words to filter for meaningful words.

```{r}
#ds with stemming and without punctuation

# First stage of cleaning, 
df$reviews <- as.character(df$reviews) %>%
  tolower() %>%
  {gsub(":( |-|o)*\\("," SADSMILE ", .)} %>%       # Find :( or :-( or : ( or :o(
  {gsub(":( |-|o)*\\)"," HAPPYSMILE ", .)} %>%     # Find :) or :-) or : ) or :o)
  {gsub("(\"| |\\$)-+\\.-+"," NUMBER", .)} %>%     # Find numbers
  {gsub("([0-9]+:)*[0-9]+ *am"," TIME_AM", .)} %>%         # Find time AM
  {gsub("([0-9]+:)*[0-9]+ *pm"," TIME_PM", .)} %>%         # Find time PM
  {gsub("-+:-+","TIME", .)} %>%                    # Find general time
  {gsub("\\$ ?[0-9]*[\\.,]*[0-9]+"," DOLLARVALUE ", .)} %>%           # Find Dollar values
  {gsub("[0-9]*[\\.,]*[0-9]+"," NUMBER ", .)} %>%           # Find remaining numbers
  {gsub("-"," ", .)} %>%                           # Remove all -
  {gsub("&"," and ", .)} %>%                       # Find general time
  {gsub("\"+"," ", .)} %>%                         # Remove all "
  {gsub("\\|+"," ", .)} %>%                        # Remove all |
  {gsub("_+"," ", .)} %>%                          # Remove all _
  {gsub(";+"," ", .)} %>%                          # Remove excess ;
  {gsub(" +"," ", .)} %>%                          # Remove excess spaces
  {gsub("\\.+","\\.", .)} %>%                       # Remove excess .
  {gsub("\\bi'v\\b", "", .)} %>%                    # Remove "i'v"
  {gsub("\\b'\\b", "", .)} %>%                       # Remove "'"
  {gsub("\\bit\\b", "", .)}                      # Remove "it"

df_tokens <- df %>%
  unnest_tokens(word, reviews) %>%
  filter(!str_detect(word, "\\d+")) %>% # exclude words with numbers
  filter(!str_detect(word, "^[[:punct:]]+$")) %>% # exclude words that are only punctuation
  anti_join(get_stopwords()) %>% # remove stopwords
  mutate(word = wordStem(word)) # Stemming
```

```{r}
# Create a list of non-meaningful words
non_meaningful_words <- c("u", "us", "on", "in", "at", "of", "is", "am",
                          "are", "was", "were", "abl","get","just", "even",
                          "number","got","via","san","atl","it","'","i'v")

# Filter out the non-meaningful words
df_tokens <- df_tokens %>%
  filter(!word %in% non_meaningful_words) %>%
  filter(nchar(word) > 2)

```

## Analysis

### Principal component analysis (PCA)

In principal component analysis (PCA), the aim is to find the components that have the highest predictive accuracy and contain the largest amount of information to describe the reviews in a high-dimensional space. Based on the top words of the first five principal components (PCs) before rotation, PC1 seems to capture time-related and logistical aspects of air travel such as waiting at the gate or contacting an agent, while PC2 focuses on the amenities and comfort offered to passengers such as seat class and lounge access. PC3 is 1 baggage-related, focused on issues like carrying and claiming luggage, while PC4 is more related to disruptions in travel plans such as cancellations or mask-wearing policies. PC5 appears to be focused on interactions with airline staff, such as booking a ticket or confirming a seat.To improve interpretability, rotation techniques such as varimax rotation were used to find dimensions or directions that have a strong relationship with a small set of words and can be viewd in Figure 1.

```{r}
# PCA

review_tdm <- t(dfm)


counts <- rowSums(as.matrix(review_tdm)) 
sortedcount <- counts%>% sort(decreasing=TRUE)
nwords<-200
sortednames <- names(sortedcount[1:nwords])

pca_results <- prcomp(t(review_tdm[1:1000,]), scale = FALSE, rank. = 50) 
pca_results_backup <- pca_results  # create a backup of results for later use

fviz_screeplot(pca_results,ncp=30)

ncomp<-5
pca_results_backup <- pca_results
```

```{r}
#select the most important words per dimension

j<-1
toplist <- abs(pca_results$rotation[,j]) %>% sort(decreasing=TRUE) %>% head(10)
topwords <- (names(toplist))
for (j in 2:ncomp){
  toplist <- abs(pca_results$rotation[,j]) %>% sort(decreasing=TRUE) %>% head(10)
  topwords <-cbind( topwords , (names(toplist)))
}

topwords

#unrotated pca plot dim 1 and 2
axeslist <- c(1, 2)
fviz_pca_var(pca_results, axes=axeslist 
             ,geom.var = c("arrow", "text")
             ,col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)


rawLoadings <- pca_results$rotation[,1:5] %*% diag(pca_results$sdev, ncomp, ncomp)
rotated <- varimax(rawLoadings)
pca_results$rotation <- rotated$loadings
pca_results$x <- scale(pca_results$x[,1:ncomp]) %*% rotated$rotmat


#select the most important words per rotated dimension

j<-1
toplist <- abs(pca_results$rotation[,j]) %>% sort(decreasing=TRUE) %>% head(10)
topwords <- (names(toplist))
for (j in 2:ncomp){
  toplist <- abs(pca_results$rotation[,j]) %>% sort(decreasing=TRUE) %>% head(10)
  topwords <-cbind( topwords , (names(toplist)))
}

topwords

pca_results_small <- pca_results
pca_results_small$x <- pca_results_small$x[1:200,] # Keep only 200 reviews to plot
pca_results <- pca_results_small
```

The top words in each of the five rotated dimensions in the plot are indicative of the main topics and aspects of air travel that are most important to customers. PC1 relates to time-related aspects like delays, waiting times, and connections. PC2 concerns the quality of services, amenities, and class of service. PC3 is about luggage handling, including check-in, claiming, and related communication with the airline. PC4 covers seating arrangements and interactions with flight attendants. Lastly, PC5 pertains to the financial aspects of air travel, such as ticket cost, class of service, and related communication with the airline.The rotated graph in Figure appears to show more meaningful and visible clusters.

```{r}
#rotated pc plot dim 1 and 2
axeslist <- c(1, 2)
fviz_pca_var(pca_results, axes=axeslist 
             ,geom.var = c("arrow", "text")
             ,col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
```

```{r}
#reviews location on pc plot 
axeslist=c(1,2)
fviz_pca_ind(pca_results, axes = axeslist,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = FALSE,     # Avoid text overlapping
             #             geom = "point" # shows only points and no lables
)

####
```

```{r}
#pca plot of dim 3 and 4
axeslist=c(3,4)
fviz_pca_var(pca_results, axes=axeslist 
             ,col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)
```

A two dimensional biplot can be utilized to display the positions of all reviews in the 2D space and
provides a more complete understanding of the relationships between the reviews and the dimensions in the rotated PCA plot. By comparing Figure 2 with the plot of the words, one can recognize the main theme of the review and the dimension it is related to. The biplot also emphasizes the reviews in each dimension and the dimensions\' interpretations by displaying what words are linked to these dimensions. This can be applied when interpreting the locations of the reviews and better comprehend of the underlying factors that drive customer perceptions and satisfaction.

```{r}
#plot of reviews on dim 3 and 4
axeslist=c(3,4)
fviz_pca_ind(pca_results, axes = axeslist, 
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)
```

```{r}
#biplot of pc 3 and 4
axeslist=c(3,4)
fviz_pca_biplot(pca_results, repel = TRUE,axes=axeslist,
                ,col.ind = "cos2" # Color by the quality of representation
                ,col.var = "contrib" # Color by contributions to the PC
)
```

### Multi- Dimensional Scaling (MDS)

By mapping words on a 2D or 3D surface and trying to maintain their relative lengths, Multidimensional
Scaling (MDS) can be used to show how similar and different words are. Three separate MDS studies were
conducted, each with a different context: one with \"document\" as the context, and two others with \"window\"
as the context, with windows of sizes 1 and 5, respectively. When the context is set to \"document,\" the plot
is established based on similarities between entire documents rather than individual words or pairs of words,
which can lead to more significant and interpretable clusters because the overall similarity of documents
containing related words and concepts can be seen. Since the plot is built from the commonalities between
individual words, when the context is set to a small window (ex. 1), wider connections between words may
be missed. When the window size is bigger (ex. 5), the plot is also based on word similarity but within
a larger context, helping to capture wider links between ideas; however, it may be challenging to identify
interpretable groups due to the inclusion of non-meaningful noise.

```{r}
{r}
##MDS

#####
# Create a corpus from the tokenized dataset
corpus <- df_tokens %>% 
  group_by(Customer_ID) %>% 
  summarise(text = paste(word, collapse = " "))

#corpus and dfm
corpus <- corpus(corpus, docid_field = "Customer_ID", text_field = "text")
dfm <- dfm(corpus)

####
# apply TF-IDF weighting
dfm <- dfm_tfidf(dfm)

# get top terms by TF-IDF
tfidf_terms <- topfeatures(dfm, n = 20)
test <- as.data.frame(tfidf_terms)
test <- rownames_to_column(test)

# plot the terms by TF-IDF
ggplot(test, aes(x = rowname, y = tfidf_terms)) + 
  geom_col(fill = "skyblue") + 
  coord_flip() + 
  labs(x = NULL, y = "TF-IDF") + 
  theme(text = element_text(size = 17)) + 
  ggtitle("Top Terms by TF-IDF")

```

```{r}
#MDS with context = "document"

# create a co-occurrence matrix
co_occurrence_matrix <- fcm(dfm, context = "document", 
                            count = "frequency", tri = FALSE)

#Need number of documents with each word on the diagonal
counts <- colSums(as.matrix(dfm))
co_occurrence_matrix <- as.matrix(co_occurrence_matrix)
diag(co_occurrence_matrix) <- counts
sortedcount <- counts %>% sort(decreasing=TRUE)
sortednames <- names(sortedcount)
nwords <- 200
subset_words <- names(sortedcount[1:nwords])
dfm_subset <- dfm_select(dfm, pattern = names(sortedcount[1:nwords]))
co_occurrence_matrix_window <- fcm(dfm_subset, context = "document", 
                                   count = "frequency", tri = FALSE)

diag(co_occurrence_matrix_window) <- colSums(as.matrix(dfm_subset))
co_occurrence_matrix_window[1:15, 1:15]
```

```{r}
# Transform similarities to distances
distances <- sim2diss(co_occurrence_matrix_window, method = "cooccurrence")

# Find the best matching coordinates in a 2D map given the distances
MDS_map <- smacofSym(distances)

# Plot the MDS map
ggplot(as.data.frame(MDS_map$conf), aes(D1, D2, label = rownames(MDS_map$conf))) +
  geom_text(check_overlap = TRUE) +
  theme_minimal(base_size = 15) +
  xlab('') + ylab('') +
  scale_y_continuous(breaks = NULL) +
  scale_x_continuous(breaks = NULL)
```

```{r}
#MDS with context = "window" and window=1


# create co-occurrence matrix with window size 1
co_occurrence_matrix <- fcm(df_tokens$word, context = "window", window_size = 1)

co_occurrence_matrix<-co_occurrence_matrix[sortednames[1:nwords],sortednames[1:nwords]]

diag(co_occurrence_matrix) <- counts[sortednames[1:nwords]]
co_occurrence_matrix[1:15,1:15]

distances <- sim2diss(co_occurrence_matrix, method = "cooccurrence") # Transform similarities to distances.
min(distances) #check whethet minimum distance is positive. Sometimes the counting procedure did something unexpected.
max(distances) #check whethet minimum distance is positive. Sometimes the counting procedure did something unexpected.
MDS_map <- smacofSym(distances) # run the routine that finds the best matching coordinates in a 2D mp given the distances
ggplot(as.data.frame(MDS_map$conf), aes(D1, D2, label = rownames(MDS_map$conf))) +
  geom_text(check_overlap = TRUE) + theme_minimal(base_size = 15) + xlab('') + ylab('') +
  scale_y_continuous(breaks = NULL) + scale_x_continuous(breaks = NULL)
```

```{r}
#MDS with Window = 5

co_occurrence_matrix <- fcm(df_tokens$word, context = "window", window=5, count = "boolean", tri=FALSE)

co_occurrence_matrix<-co_occurrence_matrix[sortednames[1:nwords],sortednames[1:nwords]]

diag(co_occurrence_matrix) <- counts[sortednames[1:nwords]]
co_occurrence_matrix[1:15,1:15]

distances <- sim2diss(co_occurrence_matrix, method = "cooccurrence") # Transform similarities to distances.
MDS_map <- smacofSym(distances) # run the routine that finds the best matching coordinates in a 2D map given the distances
ggplot(as.data.frame(MDS_map$conf), aes(D1, D2, label = rownames(MDS_map$conf))) +
  geom_text(check_overlap = TRUE) + theme_minimal(base_size = 15) + xlab('') + ylab('') +
  scale_y_continuous(breaks = NULL) + scale_x_continuous(breaks = NULL)


```

This trend was seen with the results obtained as well in Figure 3, where the most interpretable plot with
the clearest clusters was the plot with the context set to \"document\". Here, four meaningful clusters have been
observed. Cluster 1 contains words related to the comfort and amenities of flying, such as \"comfort\", \"food\",
\"seat\" and \"cabin\", in addition to words related to the experience of flying, such as \"flew\", \"aircraft\". Cluster
2 contains words related to travel logistics and scheduling, such as \"delay\", \"schedule\" and \"time\",and some
words related to airport infrastructure, such as \"gate\", \"depart\", and \"arrive\". This suggests that these
words are often used together when passengers are discussing issues related to travel logistics. Group 3
contains words related to booking flights and managing travel arrangements, such as \"dollar value\", \"book\",
\"complete\", \"need\", \"home\", and \"phone\". Group 4 contains words related to lost or delayed luggage and
other travel-related issues, such as \"luggage\" and \"find\".

### 
Comparison of PCA and MDS

Both Principal Components Analysis (PCA) and Multi-Dimensional Scaling (MDS) are efficient techniques
for summarizing the fundamental structure of word vector data, but their methodologies and results vary.
One dimension is produced by PCA for each component, which can make it challenging to decipher and
necessitate numerous plots to fully comprehend. In spite of this, PCA offers characteristics that can be
applied to prediction tasks and enables reviews to be summed up with ratings on different components. A review can be thought of as the combination of all the lines in the graph, which indicate the existence of themes in the reviews. MDS, on the other hand, can offer a simpler two-dimensional representation that can be seen as a singular image. It summarizes the word groups that reflect prevalent topics in reviews and the structure derived from similarity data. The inability to place or summarize reviews in \"MDS\" space makes it more difficult to look at reviews as a whole. PCA offered a better visualization than MDS, based on the results obtained. PCA made it simpler to identify significant and interpretable clusters of terms that were more closely linked to one another.

### Sentence Based Sentiment Analysis using the Polarity Algorithm

Sentiment analysis was performed on the uncleaned Delta Airlines review dataset, without stemming and
including punctuation, using the Jockers & Rinker dictionary. Due to the fact that the sentiment analysis was
performed on sentences base the sentiment score was performed as the average sentiment of each individual
word sentiment. In Figure 4 we can see a histogram and the density of positive and negative reviews. The
negative reviews out count the positive ones. Moreover we can see a small overlap around a value of 0 in the
sentiment score due to the fact that those reviews are more neutral but we executed our analysis with on
only two categories of sentiments.

```{r}
#Loading the data as new 
df <- read.csv("C:/Users/ioann/Desktop/Delta_Airline_Review_Dataset-Asof02172023.csv")
reviews_df <- df
#Removing the uneccesary part of the reviews.
reviews_df$reviews <- gsub(".*\\|", "", reviews_df$reviews) 
```

```{r}
# Determine sentiments following the Hu and Liu dictionary
reviews_df$sent <- sentiment_by(get_sentences(reviews_df[,"reviews"]))$ave_sentiment

#Visualizations
library(ggplot2)

# Get positive reviews: Sentiment score that is higher than 0
pos_reviews      <- reviews_df %>% filter( reviews_df[,"sent"] > 0)
# Get negative reviews: Sentiment score that is bellow 0
neg_reviews      <- reviews_df %>% filter( reviews_df[,"sent"] < 0)

# Determine the average sentiment scores in positive reviews and negative reviews
for (v in c("sent")){
  cat(v)
  cat(" ", mean(neg_reviews[, v]), " ", mean(pos_reviews[, v]), "\n")
}
```

```{r }
# Histogram showing the distribution of different (both positive and negative) sentiment scores
ggplot(data = reviews_df ,aes(sent)) +
  geom_histogram(aes(fill = "Positive"),   data = pos_reviews, alpha = 0.5) +
  geom_histogram(aes(fill = "Negative"), data = neg_reviews, alpha = 0.5) +
  scale_colour_manual("Sentiment", values = c("green", "red"), aesthetics = "fill")
```

```{r}
# Plot sentiment scores for positive and negative reviews
ggplot() +
  geom_density(data = pos_reviews, aes(x = sent, fill = "Positive"), alpha = 0.5) +
  geom_density(data = neg_reviews, aes(x = sent, fill = "Negative"), alpha = 0.5) +
  scale_fill_manual(values = c("Positive" = "blue", "Negative" = "red")) +
  ggtitle("Distribution of Sentiment Scores in Positive and Negative Reviews") +
  xlab("Sentiment Score") +
  ylab("Density")
```

Comparing the results of our analysis to the star rating of the data set in Figure 5, it is clear that the
sentiment score does not follow the star rating. After investigating many individual reviews we figure out
that the rating that was given to a review was quite incorrect. For example, a review that had a negative
sentiment intuitively, had been given a star rating of 8. We can conclude that the star rating is not reliable
and it is a big limitation of our data set.

```{r}
# plot sentiment based on star rating

ggplot(reviews_df, aes(x = factor(star.rating), y = sent, fill = factor(star.rating))) +
  geom_violin() +
  geom_boxplot(width=0.1, fill="white", outlier.shape=NA) +
  labs(x = "Star Rating", y = "Sentiment Score", title = "Sentiment Score by Star Rating") +
  theme_minimal()




# Determine sentiments  ignoring amplifications
reviews_df$sent_noamp <- sentiment_by(get_sentences(reviews_df[,"reviews"]),
                                            hyphen = "",
                                            amplifier.weight = 0.0, n.before = 5, n.after = 2,
                                            question.weight = 1, but.weight = 0.0, missing_value = 0,)$ave_sentiment




# Plot the sentiment scores from both dictionaries, with and without negations and amplifications
par(mfrow = c(2,1))
hist(reviews_df$sent, main = " Dictionary (with negations and amplifications)")
hist(reviews_df$sent_noamp, main =  "Dictionary (without negations and amplifications)")
```

To continue we experimented with the settings of the sentiment analysis algorithm if it would affect the
sentiments for the reviews. We first ignored the amplifiers and after that we set the weight of the amplifiers to 3. On both scenarios we obtained almost similar results as it is evidenced from Figure 6 with our initial result as we got coefficients of 0.98 and 0.95 respectively.

```{r}
# Calculate the correlation between the original sentiment scores and the sentiment scores that ignore negations and amplifications
cor(reviews_df$sent, reviews_df$sent_noamp)

# Determine sentiments with amplifier weight set at 3
reviews_df$sent_amp <- sentiment_by(get_sentences(reviews_df[,"reviews"]),
                                            hyphen = "",
                                            amplifier.weight = 3.0, n.before = 5, n.after = 2,
                                            question.weight = 1, but.weight = 0.0, missing_value = 0,)$ave_sentiment
cor(reviews_df$sent, reviews_df$sent_amp)
par(mfrow = c(2,1))
hist(reviews_df$sent, main = " Dictionary (with negations and amplifications)")
hist(reviews_df$sent_amp, main =  "Dictionary (with amplifers wieght set to 3)")

```

Figure 7 demonstrates the most frequent words in positive and negative reviews respectively.

```{r}
#Wordclouds

library(tm)
library(wordcloud)
library(RColorBrewer)

# Create a function to clean and preprocess the corpus
clean_corpus <- function(corpus) {
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, removeWords, stopwords("english"))
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

# Create a corpus for positive reviews
pos_corpus <- Corpus(VectorSource(pos_reviews$reviews))
pos_corpus <- clean_corpus(pos_corpus)

# Get the frequency of the words in the corpus
pos_freq <- sort(colSums(as.matrix(DocumentTermMatrix(pos_corpus))), decreasing = TRUE)

# Generate a word cloud
set.seed(123)
wordcloud(words = names(pos_freq), freq = pos_freq, min.freq = 20, max.words = 200, random.order = FALSE, colors = brewer.pal(8, "Dark2"))
```

```{r}
# Create a corpus for negative reviews
neg_corpus <- Corpus(VectorSource(neg_reviews$reviews))
neg_corpus <- clean_corpus(neg_corpus)

# Get the frequency of the words in the corpus
neg_freq <- sort(colSums(as.matrix(DocumentTermMatrix(neg_corpus))), decreasing = TRUE)

# Generate a word cloud for negative reviews
set.seed(123)
wordcloud(words = names(neg_freq), freq = neg_freq, min.freq = 20, max.words = 200, random.order = FALSE, colors = brewer.pal(8, "Dark2"))

```

### Latent Dirichlet Allocation (LDA)

In the fourth stage of the analysis, a Latent Dirichlet Allocation (LDA) was contacted on the Delta airline
dataset. LDA is a soft clustering method, because a term can belong to multiple topics and a document can be about multiple topics. In comparison with the hard clustering method, where an object is allocated to one single cluster. In LDA it is necessary to find the optimal number of topics K. There are two methods that can be used to estimate the topics. A Variational estimation was used. Moreover, to find the optimal number of topics K, a balance in the in-sample fit with the model complexity is needed. To find the a perplexity of a set of documents was used.
The optimal number of topics is 5. Afterwards with the use of a search grid for hyperparameter tuning
the optimal alpha was 1.Before tuning the models perplexity was way too high but, after tuning the final
model had a perplexity of approximately 677.In Figure 8 below, 5 topics can be seen. Each topic can be
given a name, by looking at the most important terms in the topic. The first topic is called Punctuality,
because the most important terms in this topic are: flight, delay, delta, hour, time. The second topic is
named Comfort, because the most important terms are: seat, flight, class and food. The third topic is named Customer Service, because the most important terms are: delta, hour, told, call and ticket. The fourth topic is called Airline, because of the words airline, service, check, bag. The fifth topic is called, Boarding, because the words: gate, board, seat, plane, indicate that these reviews might be about the boarding process.

```{r}
# Load required packages
library(tidyverse)
library(tidytext)
library(topicmodels)
library(dplyr)
library(SnowballC)
library(ggplot2)

# train test split 

set.seed(123)

train_index <- sample(nrow(reviews_df), 0.8 * nrow(reviews_df))
train_data <- reviews_df[train_index, ]
test_data <- reviews_df[-train_index, ]

# document-term matrices for train and test sets
train_dtm <- train_data %>%
  unnest_tokens(word, reviews) %>%
  anti_join(stop_words) %>% 
  filter(str_detect(word, "^[a-zA-Z]+$")) %>% 
  mutate(word = wordStem(word, language = "porter")) %>%
  count(Customer_ID, word, sort = TRUE) %>%
  cast_dtm(Customer_ID, word, n)

test_dtm <- test_data %>%
  unnest_tokens(word, reviews) %>%
  anti_join(stop_words) %>% 
  filter(str_detect(word, "^[a-zA-Z]+$")) %>% 
  mutate(word = wordStem(word, language = "porter")) %>% 
  count(Customer_ID, word, sort = TRUE) %>%
  cast_dtm(Customer_ID, word, n)

# Set the number of topics 
num_topics <- 5

# LDA model with VEM
lda_model <- LDA(train_dtm, num_topics, 
                 doc_word_count = apply(train_dtm, 1, sum),
                 control = list(seed = 1234,
                                alpha = 0.1,
                                em = list(iter.max = 1000, tol = 0.001)))

# search grid for hyperparameters
search_grid <- expand.grid(alpha = seq(0.1, 1, by = 0.1),
                           iter.max = c(1000, 2000, 3000))

# function to evaluate model with given hyperparameters
evaluate_model <- function(alpha, iter.max) {
  model <- LDA(train_dtm, num_topics, 
               doc_word_count = apply(train_dtm, 1, sum),
               control = list(seed = 1234,
                              alpha = alpha,
                              em = list(iter.max = iter.max, tol = 0.001)))
  perplexity <- perplexity(model, test_dtm)
  return(perplexity)
}

# evaluate all models in the search grid
perplexity_scores <- apply(search_grid, 1, function(params) {
  evaluate_model(params[["alpha"]], params[["iter.max"]])
})

#  best hyperparameters
best_params <- search_grid[which.min(perplexity_scores),]
best_perplexity <- min(perplexity_scores)

# train the final model with the best hyperparameters
final_model <- LDA(train_dtm, num_topics, 
                   doc_word_count = apply(train_dtm, 1, sum),
                   control = list(seed = 1234,
                                  alpha = best_params[["alpha"]],
                                  em = list(iter.max = best_params[["iter.max"]], tol = 0.001)))


perplexity <- perplexity(final_model, newdata = test_dtm)
cat("Perplexity:", perplexity, "\n")

# Most important terms for each topic
lda_terms <- tidy(final_model, matrix = "beta") %>%
group_by(topic) %>%
top_n(10, beta) %>%
ungroup() %>%
arrange(topic, -beta)

# Bar plot of the most frequent terms for each topic
ggplot(lda_terms, aes(x = reorder(term, beta), y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  labs(x = "Term", y = "Beta", title = "Top 10 terms by topic") +
  facet_wrap(~topic, scales = "free") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
                 
# Print 
lda_terms
                 

# Calculate perplexity on train and test sets
train_perplexity <- perplexity(final_model, newdata = train_dtm)
test_perplexity <- perplexity(final_model, newdata = test_dtm)

# Create a data frame for plotting
perplexity_df <- data.frame(
  dataset = c("Train", "Test"),
  perplexity = c(train_perplexity, test_perplexity)
)

# Create the plot
ggplot(perplexity_df, aes(x = dataset, y = perplexity)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Perplexity by Dataset",
       x = "Dataset",
       y = "Perplexity")


```

## 
Conclusions

In conclusion, the analysis of Delta airline reviews using techniques such as PCA, MDS, Sentiment Analysis, and LDA provided insights into customer opinions and identified important topics discussed in the reviews. Through PCA, the main themes and aspects of air travel that were most important to customers were identified, and MDS was used to show how similar and different words were. The sentiment analysis revealed that customers\' overall sentiment towards Delta airline was mostly negative. Finally, LDA helped to identify specific topics within the reviews, such as flight booking and customer service. These techniques provide valuable insights for businesses looking to understand customer feedback and improve their products or services.



